Title

### 2013-03-05 inc/extension/initial_conditions/bin_model_figure.tex
all notes from andreas included for initial conditions section

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:bin_model_acc}
      \begin{tikzpicture}
        \input{Acc}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:bin_model_vmax}
      \begin{tikzpicture}
        \input{Vmax}
      \end{tikzpicture}
    }
    \\
  }
  \centerline{
    \subfloat[][]{
      \label{fig:bin_model_equal}
      \begin{tikzpicture}
        \input{Equal}
      \end{tikzpicture}
    }
  }
  \caption[Results of bin model for computing initial conditions]{
    Comparison of the results of the bin model and AG model allowed functional forms for three different input parameters cases.
    Compared are: \subref{fig:bin_model_acc} the DC acceleration dominated case, \subref{fig:bin_model_vmax} the photoemission energy dominated case, and \subref{fig:bin_model_equal} an intermediate case.
    For $\sigma_z$ (red) and $\gamma_z$ (green) the simulated data (solid) and the fit to the AG allowed form (dashed) are decently well matched in all cases.
    Unfortunately, the model only allows for a constant $\eta_z$ (green) and in all but the extreme acceleration dominated case \subref{fig:bin_model_acc} the model cannot well represent the simulated data.
  }
  \label{fig:bin_model}
\end{figure}

>>>>

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:bin_model_acc}
      \begin{tikzpicture}
        \input{Acc}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:bin_model_vmax}
      \begin{tikzpicture}
        \input{Vmax}
      \end{tikzpicture}
    }
    \\
  }
  \centerline{
    \subfloat[][]{
      \label{fig:bin_model_equal}
      \begin{tikzpicture}
        \input{Equal}
      \end{tikzpicture}
    }
  }
  \caption[Results of bin model for computing initial conditions]{
    Comparison of the results of the bin model and AG model allowed functional forms for three different input parameters cases.
    Compared are: \subref{fig:bin_model_acc} the DC acceleration dominated case, \subref{fig:bin_model_vmax} the photoemission energy dominated case, and \subref{fig:bin_model_equal} an intermediate case.
    For the Gaussian spatial distribution whose variance is $\sigma_z$ (red) and the momemtum chirp $\gamma_z$ (green) the simulated data (solid) and the fit to the AG allowed form (dashed) are decently well matched in all cases.
    Unfortunately, the model only allows for a constant local momentum variance $\eta_z$ (green) and in all but the extreme acceleration dominated case \subref{fig:bin_model_acc} the model cannot well represent the simulated data.
  }
  \label{fig:bin_model}
\end{figure}

### 2013-03-05 inc/extension/initial_conditions/initial_conditions.tex
all notes from andreas included for initial conditions section

Finally, and again from a simplistic viewpoint, only the electrons generated with positive longitudinal momentum will contribute to the pulse since those electrons generated with negative momentum do not leave the photocathode.
This implies that the final initial condition, the local momentum uncertainty in the longitudinal direction $\eta_z$, is half that of the transverse directions; that is to say
\begin{equation}
  ( \Delta p_{ z } )^{2} = \left ( \frac{\Delta p_{ x , y }}{ 2 } \right )^{2} \punct{,}
\end{equation}
so that
\begin{equation}
  \eta_{ z } ( 0 ) \approx \frac{ \eta_{ \smallT } ( 0 )}{ 4 } \punct{.}
\end{equation}

@@

We recognize that these initial conditions for an electron pulse generated by a laser-driven DC gun are idealized in that they neglect several important effects; in particular, the interplay of dispersive ($ \eta_{i}(0) \neq 0 $) and space-charge effects in the acceleration region of the photoelectron gun and transverse and longitudinal effects due to the divergence of the DC field in the vicinity of the gun anode.\cite{berger_dc_2009,togawa_ceb6_2007}
Such effects and the limits of the validity of \ref{eq:initial_sigma_z}, within the context of the AG model, will be presented in Section \ref{sec:bin_model}.
However, \ref{eq:summary} also represent a defined set of initial conditions that allows the effect of electron optics (i.e., magnetic lenses and RF cavities) on electron pulse propagation to be more readily understood.
Moreover, they reflect the fact that the majority of DC photoelectron guns are driven by laser pulses with spatial and temporal profiles that are close to Gaussian.\cite{williamson_clocking_1997,sciaini_electronic_2009}
Only for specialized cases, such as the generation of uniform ellipsoid electron bunch shapes, is spatial and temporal manipulation of the incident laser pulse considered.\cite{luiten_how_2004,li_generating_2008}

@@

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_0 N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital spatial uncertainty in the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as allowed by the AG model), we can determine the velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally the velocity uncertainty in each pulse can be computed, however unlike the previous parameters, the AG model only allows for a constant value of local momentum uncertainty across the pulse $\eta_z(0)$.
\ref{fig:bin_model} shows that this limitation on functional form severely limits the accuracy with which the determined value of $\eta_z(0)$ represents the actual distribution of momentum uncertainties computed by the binning model.

Additionally the iterative time-step analysis clearly demonstrates that the local longitudinal momentum variance $ \eta_{ z } $ is not constant over the inital photo-generated electron bunch.
In fact, $ \sqrt{ \eta_{ z } ( 0 ) } $ varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch with the narrowest momentum distribution at the front of the bunch where only the faster electrons with velocity near $ v_{ 0 } $ initially reside.
Unfortunately, the self-similar theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch; to allow a more realistic fit to the simulated initial data, the pulse would eventually evolve to be non-Gaussian.
%Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $: indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.

>>>>

Finally, and again from a simplistic viewpoint, only the electrons generated with positive longitudinal momentum will contribute to the pulse since those electrons generated with negative momentum do not leave the photocathode.
This implies that the final initial condition, the local momentum uncertainty in the longitudinal direction $\eta_z$, is half that of the transverse directions; that is to say
\begin{equation}
  ( \Delta p_{ z } )^{2} = \left ( \frac{\Delta p_{ x , y }}{ 2 } \right )^{2} \punct{,}
\end{equation}
so that
\begin{equation}
  \eta_{ z } ( 0 ) \approx \frac{ \eta_{ \smallT } ( 0 )}{ 4 } \punct{,}
\end{equation}
which is certainly expected to be reasonably accurate in the short-pulse limit, where the acceleration has had no effect (see Section \ref{sec:bin_model} for further investigation).

@@

We recognize that these initial conditions for an electron pulse generated by a laser-driven DC gun are idealized in that they neglect several important effects; in particular, the interplay of dispersive ($ \eta_{i}(0) \neq 0 $) and space-charge effects in the acceleration region of the photoelectron gun and transverse and longitudinal effects due to the divergence of the DC field in the vicinity of the gun anode.\cite{berger_dc_2009,togawa_ceb6_2007}
Such effects and the limits of the validity of the longitudinal terms of \ref{eq:summary}, within the context of the AG model, will be presented in Section \ref{sec:bin_model}.
However, \ref{eq:summary} also represent a defined set of initial conditions that allows the effect of electron optics (i.e., magnetic lenses and RF cavities) on electron pulse propagation to be more readily understood.
Moreover, they reflect the fact that the majority of DC photoelectron guns are driven by laser pulses with spatial and temporal profiles that are close to Gaussian.\cite{williamson_clocking_1997,sciaini_electronic_2009}
Only for specialized cases, such as the generation of uniform ellipsoid electron bunch shapes, is spatial and temporal manipulation of the incident laser pulse considered.\cite{luiten_how_2004,li_generating_2008}

@@

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_0 N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the inital photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{ 0 } $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to seperate from one another.

This limitation on functional form severely limits the accuracy with which the determined value of $\eta_z(0)$ represents the actual distribution of momentum uncertainties computed by the binning model.
The self-similar theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch; with a more realistic fit to the simulated initial data, the pulse would eventually evolve to be non-Gaussian.
%Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $: indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.
